Comparing R packages for calculation of persistent homology

### 2019-12-16 tdabench-paper/tdabench.Rmd
Add most affiliations

---
title: Comparing efficiency of R packages implementing calculation of persistent homology
author:
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author1@work
  - name: Author Two
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

@@

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).
\bibliography{RJreferences}

>>>>

---
title: Comparing R packages for calculation of persistent homology
author:
  - name: Eashwar V. Somasundaram
    affiliation: School of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44016
    email: eashwar.somasundaram@case.edu
  - name: Shael E. Brown
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    email: shael.brown@mail.mcgill.ca
  - name: Adam Litzler
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195
    email:  author@work
  - name: Raoul R. Wadhwa
    affiliation: Cleveland Clinic Lerner College of Medicine
    address:
    - Case Western Reserve University
    - Cleveland, OH 44195
    email: raoul.wadhwa@case.edu
  - name: Jacob G. Scott
    affiliation: Department of Translational Hematology and Oncology Research
    address:
    - Cleveland Clinic Foundation
    - Cleveland, OH 44195
    email: ScottJ10@ccf.org
abstract: >
  An abstract of less than 150 words.
output:
  rticles::rjournal_article:
    includes:
      in_header: preamble.tex
---

@@

Introductory section which may include references in parentheses
\citep{Rlang}, or cite a reference such as \citet{Rlang} in the text.

@@

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).
\bibliography{tdabench}
